# Abschließende Bemerkungen

Einige Hinweise für *`selbständige`* Textanalysen. 🤗

{{ \< include \_WM_Presentation.qmd \> }}

## Callout Types

::: {.callout-note}
Note that there are five types of callouts, including: `note`, `warning`, `important`, `tip`, and `caution`.
:::

::: callout-tip
## Tip With Caption / Tipp mit Titel

This is an example of a callout with a caption.
:::

::: callout-important
Das ist wichtig.
:::

::: callout-warning
Warning
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

## DiagrammeR mermaid

```{r}
library(DiagrammeR)
# https://rich-iannone.github.io/DiagrammeR/mermaid.html

mermaid("
graph LR
  A-->B
  A-->C
  C-->E
  B-->D
  C-->D
  D-->F
  E-->F
")
```

```{r}
mermaid("graph LR; A-->B; A-->C; C-->E; B-->D; C-->D; D-->F; E-->F")
```

```{r}
mermaid("graph TB; A-->B; A-->C; C-->E; B-->D; C-->D; D-->F; E-->F")
```

```{r}
mermaid("
graph LR
  A[node text]
")

mermaid("
graph LR
  A(node text)
")

mermaid("
graph LR
  A((node text))
")

mermaid("
graph LR
  A{node text}
")

mermaid("
graph LR
  A>node text]
")

mermaid("
graph LR
A(Rounded)-->B[Rectangular]
B-->C{A Rhombus}
C-->D[Rectangle One]
C-->E[Rectangle Two]
")
```

```{r}
mermaid("
sequenceDiagram
  customer->>ticket seller: ask ticket
  ticket seller->>database: seats
  alt tickets available
    database->>ticket seller: ok
    ticket seller->>customer: confirm
    customer->>ticket seller: ok
    ticket seller->>database: book a seat
    ticket seller->>printer: print ticket
  else sold out
    database->>ticket seller: none left
    ticket seller->>customer: sorry
  end
")
```
